Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2023-01-08 edubots_surveys.Rnw
Rewriting part of her answers

\textcolor{black}{This study followed a quantitative approach towards addressing its research objective, by collecting rich data about the use of messaging applications and chatbots
by educators in both universities and colleges\footnote{In Spain, they are called simply high schools, and deliver
tertiary or associated degrees that do not have the consideration of university degrees}.
To achieve this goal two online surveys were designed and developed using Google Forms
in Spanish. They are comprised of six questions focusing on demographic data
(i.e., sector, gender, degrees, discipline, age, teaching experience)
followed by several multiple choice questions allowing the participants to choose multiple answers.}

In the {\bf first survey}, the multiple choice questions are
focused on the use of messaging apps in the teaching practice, the type of chatbot use cases that teachers consider
useful for their teaching and the impact of COVID on the teaching practice; please check them out to the full extent in the Appendix.\footnote{This {\bf first survey} was made in two separate Google forms, one for
university and the other for teachers in tertiary education institutions, outside the university system (vocational training, including 1- and 2-year degrees). Questions and
responses were the same, except for the type of tertiary degrees that
were considered.}

\textcolor{black}{This survey was piloted by the authors of the paper and their colleagues before using it in the
study.  All the comments collected from this trial were incorporated in the survey.
We mainly used mailing lists, as well as Telegram groups,
to post the survey link to reach out to more educators. The university form was sent to Spanish
(mainly Andaluc\'{\i}a and Galicia) universities, and also  universities in Costa Rica and
Mexico. The tertiary (non-university/college) teachers were based mainly in
Andaluc\'{\i}a. Dissemination and answers took place in the first quarter of
2021, during the Covid-19 pandemic and while, at least in Spain, many universities had
mandatory virtual teaching.}

>>>>

This study has employed a quantitative approach in order to address its research objective. A good amount of data was collected on the usage of messaging applications and chatbots by educators in universities and colleges.\footnote{In Spain, higher education institutions generally known elsewhere as colleges, are called simply high schools, and deliver
tertiary or associate degrees that do not have the consideration of university degrees.}
To achieve this goal two online surveys were designed and developed using Google Forms
in Spanish. They are comprised of six questions focusing on demographic data
(i.e., sector, gender, degrees, discipline, age, teaching experience)
followed by several multiple choice questions allowing the participants to choose multiple answers.

In the {\bf first survey}, the multiple choice questions are
focused on the use of messaging apps in the teaching practice, the type of chatbot use cases that teachers would consider
useful for their teaching and the impact of COVID on the teaching practice; please check them out to the full extent in the Appendix.\footnote{This {\bf first survey} was made in two separate Google forms, one for
university and the other for teachers in tertiary education institutions, outside the university system (vocational training, including 1- and 2-year degrees). Questions and
responses were the same, except for the type of tertiary degrees that
were considered.}

This survey was piloted by the authors of the paper and their colleagues before using it in the
study.  All the comments collected from this trial were incorporated in the survey.
We primarily used mailing lists and Telegram groups to disseminate the survey link so that it would reach a larger number of educators. The form addressed at university teachers was sent to Spanish
(mainly Andaluc\'{\i}a and Galicia) universities, and also  universities in Costa Rica and
Mexico. The tertiary (non-university/college) teachers who received the form were based mainly in
Andaluc\'{\i}a. Dissemination and answers took place in the first quarter of
2021, during the Covid-19 pandemic and while, at least in Spain, many universities had
mandatory virtual teaching.
